TBD

### 2021-03-22 outputs/paper/paper.Rmd
Edit Power Analysis
s8 regression model update

# install.packages ("gmodels")
library (gmodels)

@@

# Reference Code: https://rdrr.io/cran/pwr/man/ES.h.html
effectSize <- 2 * asin(sqrt(propNoMoneyReturned)) - 2 * asin(sqrt(proMoneyReturned))

@@

# code dummy variables
s8_model <- dfBehavModel %>%
  filter(cond != 0)
s8_model$cond <- ifelse(s8_model$cond == 1, 0, 1)

@@

# final table (S8)
stargazer(s8_main_result, s8_money_result, 
          title = "Reporting rates in the Money and No Money Condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Male", "Above 40", "Computer", "Coworkers", "Other Bystanders", "Constant"))

@@

```{r S9, echo = FALSE, warning = FALSE, message = FALSE}
### conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

@@

# final table
stargazer(s9_main_result, s9_uk_result, s9_poland_result, s9_usa_result, 
          title = "Reporting rates in NoMoney, Money, and Big Money condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Big Money", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```

```{r S10, echo = FALSE, warning = FALSE, message = FALSE}
### conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

@@

# final table
stargazer(s10_main_result, s10_uk_result, s10_poland_result, s10_usa_result, 
          title = "Reporting rates in Money-No Key condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money-NoKey", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```
# Discussion

>>>>

# install.packages ("gmodels")
library(gmodels)

@@

# Reference Code: https://cran.r-project.org/web/packages/pwr/pwr.pdf
effectSize <- 2 * asin(sqrt(proMoneyReturned)) - 2 * asin(sqrt(propNoMoneyReturned))

@@

# code dummy variables
s8_model <- dfBehavModel %>%
  mutate(no_money = if_else(cond == 0, 1, 0)) %>%
  mutate(money = if_else(cond != 0, 1, 0))

@@

# final table (S8)
stargazer(s8_main_result, s8_money_result, 
          title = "Reporting rates in the Money and No Money Condition", 
          header = FALSE,
          align = TRUE, 
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Male", "Above 40", "Computer", "Coworkers", "Other Bystanders", "Constant"))

@@

```{r S9, echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
### conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

@@

# final table
stargazer(s9_main_result, s9_uk_result, s9_poland_result, s9_usa_result, 
          title = "Reporting rates in NoMoney, Money, and Big Money condition",
          header = FALSE,
          align = TRUE, 
          font.size = "small",
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Big Money", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```

```{r S10, echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
### conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

@@

# final table
stargazer(s10_main_result, s10_uk_result, s10_poland_result, s10_usa_result, 
          title = "Reporting rates in Money-No Key condition", 
          header = FALSE,
          align = TRUE, 
          font.size = "small",
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money-NoKey", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```

# Discussion
